---
title: "Affectiva Data"
output: html_notebook
---


```{r}
library(tidyverse)

View(data_3_participants)
```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

To find out which value of targetA and targetB are smaller:
```{r}
data_3_participants$smaller<- ifelse(data_3_participants$targetA < data_3_participants$targetB, data_3_participants$targetA, data_3_participants$targetB)

View(data_3_participants)
```

To find out which value of targetA and targetB are larger:
```{r}
data_3_participants$larger<- ifelse(data_3_participants$targetA > data_3_participants$targetB, data_3_participants$targetA, data_3_participants$targetB)

View(data_3_participants)
```

To find the actualDifference between targetA and targetB:
```{r}
data_3_participants $ actualDifference <- data_3_participants$smaller/data_3_participants$larger

View(data_3_participants)
```

To change dbl values to numerical values:
```{r}
data_3_participants $ actualDifference <- as.numeric(as.character(data_3_participants $ actualDifference))

 data_3_participants $ input <- as.numeric(as.character(data_3_participants $ input))
```

To find the error:
```{r}
data_3_participants $ error <- data_3_participants $ actualDifference - data_3_participants $ input

View(data_3_participants)
```

To find log error:
```{r}

```


