---
title: "R Notebook"
output:
  html_document:
    toc: true
    toc_depth: 2
  html_notebook: default
  pdf_document: default
---

# notes

## 29-Jul-2017
Futzing with emotion timelines.
Merging trial and emo time data.
Lots of trouble figuring out when trials start and end.
Apparently time is "end" in the trials data, based on Shijian chat.

Made a grid of trials, w/ timeline of emotion values inside and color corresponding to error.

Using it to figure out what features may predict error.
Surprise, smile might be leads.
Focusing on `j59m5zpw` but moving to others as needed.

Filtering out [3] because they're high error and crazy on every emotion scale.

Notes on switching expressions around:
- surprise seems to come around errors; could this be yawns?
- smile interesting but not much on [2] or [1]'s errors
- expressions_lipCornerDepressor on [5]?
- expressions_jawDrop [1], [2], [5], ~ [4] [6]
- filter out [3] from analyses-- insane on every metric

Next steps:
- build models with the features above as classifiers? 
    - classifiers of what type of error?
- tinker with moving averages-- blur the trials a bit?
- build a bib of papers we want to include?

# Setup
## Libraries 

```{r}
library(tidyverse)
library(devtools)
library(ggplot2)
library(ggjoy)
require(data.table)
```


## Data load

```{r}
emo <- read.csv('data/emotion-19-Jul-2017.csv', header=TRUE)
trials <- read.csv('data/trial-19-Jul-2017.csv', header=TRUE)
survey <- read.csv('data/survey_data.csv', header=TRUE)
```


# Emotion data
## Reshape the emotion data for plotting

```{r}
emo2 <- emo %>%  
  gather(
    `emotions_joy`, 
    `emotions_sadness`, 
    `emotions_disgust`, 
    `emotions_contempt`, 
    `emotions_anger`, 
    `emotions_fear`, 
    `emotions_surprise`, 
    `emotions_valence`, 
    `emotions_engagement`, 
    key = "emotion", 
    value = "value") %>%
  select(emotion, value, time, key)
```

## Plot emotion data over time
```{r, fig.width=6, fig.asp=2}
# line chart (good)
ggplot(emo2) +
  geom_line(aes(x=time, y=value, colour=emotion)) +
  facet_wrap(~ key, nrow=1) +
  coord_flip()
```

## Emotion bar plots
```{r, fig.width=12, fig.asp=1.2, out.width = "50%"}

ggplot(emo2) +
  geom_col(aes(x=emotion, y=value, fill=emotion)) +
  ylim(-99, 99) +
  facet_wrap(~ key, ncol=2)
#  geom_line(aes(x=time, y=value, colour=emotion)) +
#  coord_flip()


```

## Transform Test: Moving Averages of Emotion Data
```{r, fig.width=6, fig.asp=0.618}
library(zoo)

# valence MA
emo %>% 
  arrange(key,time) %>%
  mutate(valence_ma=rollapply(emotions_valence,10,mean,align='right',fill=NA)) %>% 
  gather(
    `emotions_valence`, 
    `valence_ma`, 
    key = "emotion", 
    value = "value") %>%
  select(emotion, value, time, key) %>% 
  ggplot() + 
    geom_line(aes(x=time, y=value, colour=emotion)) +
    facet_wrap(~ key, ncol=1)

```

# Trial data
## Trial transforms

```{r}
# log transform
trials$logError <- log2(abs(trials$input*100 - trials$actualDiff*100) + 1/8)
trials$logError[trials$logError == -3] <- 0

# participant puts 50, actual is 70, should be -20
# participant puts 50, actual is 30, should be +20
trials$rawError <- trials$input*100 - trials$actualDiff*100 

# quantile filter
#trials %>% 
#  group_by(key) %>% 
#  filter( quantile(rawError, 0.25) < rawError & quantile(rawError, 0.75) > rawError )

# verify
summary(trials$logError)
summary(trials$rawError)

```

## Plot trial performance per participant
```{r, fig.width=6, fig.asp=2}
ggplot(trials, aes(x=chartType, y=logError)) +
  geom_point( alpha=1/10 ) +
  stat_summary(fun.data="mean_cl_boot", colour="red", size=0.5) + 
  facet_wrap(~ key, ncol=1)
```



# Trials and Emotion
## Joining Trials and Emotion

```{r, fig.width=6, fig.asp=0.618}

emo %>% 
  arrange(key,time) %>%
  mutate(engagement_ma=rollapply(emotions_engagement,10,mean,align='right',fill=NA)) %>% 
  mutate(valence_ma=rollapply(emotions_valence,10,mean,align='right',fill=NA)) %>% 
  group_by(key) %>% 
  summarise(
    average_engagement_ma = mean(engagement_ma, na.rm=TRUE),
    average_valence_ma = mean(valence_ma, na.rm=TRUE),
    average_engagement = mean(emotions_engagement, na.rm=TRUE),
    average_valence = mean(emotions_valence, na.rm=TRUE),
    variance_engagement = var(emotions_engagement, na.rm=TRUE),
    variance_valence = var(emotions_valence, na.rm=TRUE),
    variance_engagement_ma = var(engagement_ma, na.rm=TRUE),
    variance_valence_ma = var(valence_ma, na.rm=TRUE)
  ) %>% 
  left_join(trials, by="key") %>% 
  group_by(key) %>% 
  filter(  ) -> emo_mod 
#  filter( chartType!="Bubble" ) -> emo_mod 

```

## Exploring correlations trial-level
```{r, fig.width=6, fig.asp=0.618}
library(corrr)

# correlation summary
cor(emo_mod$rawError, emo_mod$average_valence)
# fit summary variance and valence
fit <- lm(rawError ~ average_valence, data=emo_mod)
summary(fit)

emo_mod %>% 
  ggplot(aes(x=variance_valence_ma, y=rawError)) + 
    geom_point( )

emo_mod %>% 
  ungroup() %>% 
  select(average_engagement, average_valence, variance_engagement, variance_valence, logError, rawError) %>% 
  correlate() %>% rearrange() %>% shave() %>% fashion()
```

## Roll trial data into participant-level data
```{r}
emo_mod %>% 
  summarise(
    variance_raw = var(rawError),
    mean_raw = mean(rawError),
    variance_error = var(logError),
    mean_error = mean(logError),
    valence = mean(average_valence),
    var_valence = mean(variance_valence),
    engagement = mean(average_engagement),
    var_engagement = mean(variance_engagement)
  ) -> emo_table

emo_table %>% arrange(var_valence)
```

## Exploring correlations participant-level
```{r, fig.width=6, fig.asp=0.618}

# correlation summary
cor(emo_table$mean_error, emo_table$valence)
# fit summary variance and valence
fit <- lm(mean_error ~ valence, data=emo_table)
summary(fit)

# plot error and valence
emo_table %>% 
  ggplot(aes(x=variance_raw, y=var_valence)) + 
    geom_point( )

emo_table %>% select(-key) %>% correlate() %>% rearrange() %>% shave() %>% fashion()
emo_table %>% select(-key) %>% correlate() %>% rplot()
emo_table %>% select(-key) %>% correlate() %>% network_plot(min_cor = .5)
```

# Spare
## Streamgraph
```{r eval=FALSE}
#library(streamgraph)
# streamgraph (SLOOOOOOOOOW do not run)
#emo2 %>%
#  streamgraph("emotion", "value", "time", scale="continuous") %>%
#  sg_legend(show=TRUE, label="Emotions")
```

## Time reshape attempt
```{r time_reshape, fig.width=6, fig.asp=1}

shift <- function(x, n){
  c(x[-(seq(n))], rep(NA, n))
}

# needed to reverse this. minus time for first one, shift differently, etc.
# make start variable
#trials$start <- trials$time
## shift values "up" to make end variable
#trials$end <- shift(trials$start, 1)
## take care of the NA this makes at the end (nothing to shift up from)
#trials$end[is.na(trials$end)] <- trials$start[is.na(trials$end)]
## add a buffer of 10 to the end of the last trial
#trials$end[trials$start - trials$end > 0] <- trials$start[trials$start - trials$end > 0] + 10

trials %>% 
  select(key, num, time, start, end)

# make trial end variable
trials$end <- trials$time
# shift values "down" to make start variable
trials <- trials %>% 
  mutate(
    start = lag(end)
  )
# take care of the NA this makes at the start (nothing to shift up from)
trials$start[is.na(trials$start)] <- trials$end[is.na(trials$start)] - 10
# add a buffer of 10 to the end of the last trial
trials$start[trials$start - trials$end > 0] <- trials$end[trials$start - trials$end > 0] - 10


gt <- trials %>% 
  group_by(key, start, end)

# repeat the above for emotions dataset, 3sec buffer at end
emo$start <- emo$time
# shift values "up" to make end variable
emo$end <- shift(emo$start, 1)
# take care of the NA this makes at the end (nothing to shift up from)
emo$end[is.na(emo$end)] <- emo$start[is.na(emo$end)]
# add a buffer of 10 to the end of the last trial
emo$end[emo$start - emo$end > 0] <- emo$start[emo$start - emo$end > 0] + 3

ge <- emo %>% 
  group_by(key, start, end)

# this only goes +1 second for end time. not ideal
#gt <- trials %>%
#  group_by(key) %>% 
#  mutate(start=floor(time),
#         end=ifelse(ceiling(time)==start,start+1,ceiling(time))) %>%
#  group_by(start,end) 

#ge <- emo %>%
#  group_by(key) %>% 
#  mutate(start=floor(time),
#         end=ifelse(ceiling(time)==start,start+1,ceiling(time))) %>%
#  group_by(start,end) 

ge <- data.table(ge)
gt <- data.table(gt)

setkey(ge, key, start, end)
joined <- foverlaps(gt, ge, type="any") ## return overlap join

View(joined)

grouped <- joined %>% 
  filter(key!=ppl[3]) %>% 
  group_by(key, num, chartType) %>% 
  summarise(
    mean_valence = mean(emotions_valence),
    var_valence = var(emotions_valence),
    mean_engagement = mean(emotions_engagement),
    mean_abs_valence = mean(abs(emotions_valence)),
    mean_jaw_drop = mean(expressions_jawDrop),
    var_jaw_drop = var(expressions_jawDrop),
    logError = mean(logError),
    rawError = mean(rawError)
  )
```

## Emotion timelines

```{r trial_emotion_timelines, fig.width=6, fig.asp=2}

ppl <- c("j59m5fjj", "j59m2hq1", "j58ihqdp", "j58ig5vm", "j59m5zpw", "j59lxylj")

names(emo)
  




joined %>% 
  filter(key==ppl[1]) %>% 
  ggplot(aes(x=time, y=expressions_lipStretch)) +
    geom_rect(aes(fill = rawError),
        xmin = -Inf,xmax = Inf,
        ymin = -Inf,ymax = Inf, alpha = 0.1) +
    scale_fill_gradient2() +
    geom_line() +
    facet_wrap(~ num, scales = "free_x", ncol=4)

```

```{r trial_emotion_plots, fig.width=6, fig.asp=0.618}

grouped %>% 
  ggplot( aes(x=var_jaw_drop, y=abs(rawError)) ) +
    geom_point() +
#    stat_summary(fun.data="mean_cl_boot", colour="red", size=0.5) +
    geom_smooth(method=lm) +
    facet_grid(.~chartType)

# correlation summary
chartonly <- grouped %>% filter(chartType=="Bubble")
cor( chartonly$mean_jaw_drop, abs(chartonly$rawError) )
# fit summary variance and valence
fit <- lm(abs(rawError) ~ mean_jaw_drop, data=chartonly)
summary(fit)

grouped %>% 
  ggplot( aes(x=num, y=logError) ) +
    geom_point() +
    geom_smooth(method=lm) 
  
```
